---
title: "Data Science Homework 1"
author: "Keming Zhang kz2411"
date: "9/25/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

## Problem 1
```{r Set Dataframe}
#set dataframe
set.seed(1)
df <- tibble(
  normal_10 = rnorm(10, mean = 0, sd = 1),
  vec_logical = normal_10 > 0,
  vec_character = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor_10 = factor(c("l","m","n","l","m","n","l","m","m","l"))
)
```

```{r Take the mean of each variable and print out}
mean_normal <-  mean(pull(df, "normal_10"))
mean_normal

mean_logical <-  mean(pull(df, "vec_logical"))
mean_logical

mean_character <- mean(pull(df, "vec_character"))
mean_character

mean_factor <- mean(pull(df, "vec_factor_10"))
mean_factor
```

The mean of a random sample and a logical vector work. The mean of a character vector and a factor vector do not work.

```{r Use as.numeric, eval = FALSE}
#convert logical
as.numeric(pull(df, "vec_logical"))

#convert character
as.numeric(pull(df, "vec_character"))

#convert factor
as.numeric(pull(df, "vec_factor_10"))
```

as.numeric function succeeds to convert logical and factor variables, but fails to convert character vector.  
Because it is the setting of as.numeric function that it cannot convert the character strings except it is composed of the character of number.  
It helps. When taking the mean, R will convert logical variables into numeric variables automatically, except character and factor variables.

## Problem 2
```{r load data}
data("penguins",package = "palmerpenguins")
```

The data in this dataset is about penguins. The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.
There are `r length(names(penguins))` variables in the dataset.  
They are `r names(penguins)`. And their types successively are `r class(pull(penguins,1))`, `r class(pull(penguins,2))`, `r class(pull(penguins,3))`, `r class(pull(penguins,4))`, `r class(pull(penguins,5))`, `r class(pull(penguins,6))`, `r class(pull(penguins,7))` and `r class(pull(penguins,8))`.  
The mean flipper length is `r mean(pull(penguins,"flipper_length_mm"), na.rm = TRUE)`mm.

```{r scatterplot}
scatterplot <- ggplot(penguins,aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point(na.rm = TRUE) +xlab("Bill Length (mm)") + ylab("Flipper Length (mm)")
scatterplot
ggsave("./scatterplot.png", scatterplot)
```


