---
title: "Data Science Homework 1"
author: "Keming Zhang"
date: "9/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(dplyr)
```

## Problem 1
```{r Set Dataframe}
#set dataframe
set.seed(1)
df <- tibble(
  normal_10 = rnorm(10, mean = 0, sd = 1),
  vec_logical = normal_10 > 0,
  vec_character = c("a","b","c","d","e","f","g","h","i","j"),
  vec_factor_10 = factor(c("l","m","n","l","m","n","l","m","m","l"))
)
```

```{r Take the mean of each variable and print out}
mean_normal <-  mean(pull(df, "normal_10"))
mean_normal

mean_logical <-  mean(pull(df, "vec_logical"))
mean_logical

mean_character <- mean(pull(df, "vec_character"))
mean_character

mean_factor <- mean(pull(df, "vec_factor_10"))
mean_factor
```

The mean of a random sample and a logical vector work. The mean of a character vector and a factor vector do not work.

```{r Use as.numeric, eval = FALSE}
#convert logical
as.numeric(pull(df, "vec_logical"))

#convert character
as.numeric(pull(df, "vec_character"))

#convert factor
as.numeric(pull(df, "vec_factor_10"))
```

as.numeric function succeed to convert logical and factor variables, but fail to convert character vector.

## Problem 2
```{r }
data("penguins",package = "palmerpenguins")
```

The data in this dataset is about penguins. There are `r length(names(penguins))` variables in the dataset. They are `r names(penguins)`, and their types successively are `r apply(penguins,2,class)`, 

